---
title: "Duval's FloridaHealthFinder Data"
format: html
editor: visual
---

## FloridaHealthFinder

*a service of the Agency for Health Care Administration)*

The code below takes the .csv file exported from the **Facility/Provider Locator** and creates a table with the counts by facility type used Duval County's Community Health Assessment.

The following filters were used:

-   Facility/Provider Type: "ALL TYPES"

-   County: "Duval"

## Load packages

```{r, message=FALSE}
library(tidyverse)
library(gt)
library(scales)
```

## Load data

```{r, message=FALSE, warning=FALSE}
fl_health_finder <- read_csv("2023-02-21_FloridaHealthFinder-FacilityLocator.csv")
```

## Create table

```{r}
# Create a new dataframe with the three columns needed

fl_health_finder_s <- fl_health_finder %>%
  select(`Facility Type`, Name, `License Status`)

# Create the counts by the selection of facility types:

#'Adult Day Care Center
#'Ambulatory Surgical Care Center
#'Assisted Living Facility
#'Birthing Center
#'Clinical Laboratory
#'Health Care Clinic
#'Home Health Agency
#'Home Medical Equipment Provider
#'Hospice
#'Hospitals
#'Nursing Homes
#'Rehabilitation Agency
#'Skilled Nursing Agency
#'Transitional Living Facility

# Before creating the table, create a vector with the correct facility types:

facilty_types <-
  fl_health_finder_s %>%
  drop_na() %>%  # start by dropping empty rows (1)
  distinct(`Facility Type`) %>% #find unique facility types
  pull() %>% # create a vector
  sort() %>% # sort in alphabetical order
  .[-c(1,3,4,9:11,13,14,16,18,21,22,24:26,28)] # removed from vector

fl_health_finder_s %>%
  drop_na() %>% 
  filter(`Facility Type` %in% facilty_types) %>% 
  count(`Facility Type`) %>% 
  rename("count" = n) %>% 
  gt()
```

## Create a plot of the data

```{r plots}

fl_health_finder_s %>%
  mutate(`Facility Type` = factor(`Facility Type`)) %>% 
  drop_na() %>% 
  filter(`Facility Type` %in% facilty_types) %>% 
  count(`Facility Type`) %>% 
  rename("count" = n) %>% 
  ggplot(aes(x = reorder(`Facility Type`, count), y = count)) +
  geom_col() +
  geom_text(aes(label = comma(count)), nudge_y = 50) +
  coord_flip() +
  theme_light() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(), 
        plot.title.position = "plot") +
  scale_y_continuous(n.breaks = 8, labels = comma_format()) +
  labs(title = "Number of Duval County Licensed Health Care Facilities by Facility Type")

```

## Plot for counts below 200

```{r plots 2}

fl_health_finder_s %>%
  mutate(`Facility Type` = factor(`Facility Type`)) %>% 
  drop_na() %>% 
  filter(`Facility Type` %in% facilty_types) %>% 
  count(`Facility Type`) %>% 
  rename("count" = n) %>%
  filter(count < 200) %>% 
  ggplot(aes(x = reorder(`Facility Type`, count), y = count)) +
  geom_col() +
  geom_text(aes(label = comma(count)), nudge_y = 5) +
  coord_flip() +
  theme_light() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(), 
        plot.title.position = "plot") +
  scale_y_continuous(n.breaks = 8, labels = comma_format()) +
  labs(title = "Number of Duval County Licensed Health Care Facilities by Facility Type", subtitle = "Facility types below the 200 count")
```
